Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-05-31 Robustness-Methods-and-Results.Rmd
robustness re-render with descr

>>>>

```{r}
#| label: descrFullWideAppB

vars_full <- c(
  "Core Need" = "CoreNeed",
  "Competence" = "Competence",
  "Autonomy" = "Autonomy",
  "Relatednesss" = "Relatednesss",
  "Outgroup Interaction" = "OutgroupInteraction",
  "Accidental" = "InteractionAccidental",
  "Quality" = "Quality",
  "Attitudes NL" = "Attitude"
)

s1_MlCor_full <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 1),
    id = "PID",
    selection = setdiff(as.character(vars_full), c("InteractionAccidental", "Quality")),
    labels = setdiff(names(vars_full), c("Accidental", "Quality"))
  ) 
s2_MlCor_full <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 2),
    id = "PID",
    selection = as.character(vars_full),
    labels = names(vars_full)
  ) 
s3_MlCor_full <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 3),
    id = "PID",
    selection = as.character(vars_full),
    labels = names(vars_full)
  ) 
all_MlCor_full <- 
  MlCorMat(
    data = dt_exp_all,
    id = "PID",
    selection = as.character(vars_full),
    labels = names(vars_full)
  )

rbind(
  s1_MlCor_full %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Accidental = "",
               .before = "Attitudes NL") %>%
    add_column(Quality = "",
               .before = "Attitudes NL"),
  s2_MlCor_full %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  s3_MlCor_full %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  all_MlCor_full %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      caption = "Full Sample: Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1)))  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(s3_MlCor_full),
      "Descriptives" = nrow(s3_MlCor_full) - ncol(s3_MlCor_full)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(s1_MlCor_full)) %>%
  pack_rows("Study 2", ncol(s1_MlCor_full) + 1,
            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full))) %>%
  pack_rows("Study 3", sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full)) + 1,  
            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full))) %>%
  pack_rows("Across Studies", sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full)) + 1,  
            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full), ncol(all_MlCor_full))) %>% # fix table position
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05",
      "Interaction Intent and Interaction Quality were only measured for outgroup interactions in Study 1."
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrFullWideAppB.tex")

```{r}
#| label: descrOutWideAppB

vars_out <- c(
  "Core Need" = "CoreNeed",
  "Competence" = "Competence",
  "Autonomy" = "Autonomy",
  "Relatednesss" = "Relatednesss",
  "Practical Need" = "practical_need_dum",
  "Psychological Need" = "psychological_need_dum",
  "Accidental" = "InteractionAccidental",
  "Quality" = "Quality",
  "Attitudes NL" = "Attitude"
)

s1_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 1, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
s2_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 2, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
s3_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 3, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
all_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  )

rbind(
  s1_MlCor_out %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  s2_MlCor_out %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  s3_MlCor_out %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  all_MlCor_out %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      caption = "Outgroup Interaction Sample: Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1)))  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(s3_MlCor_out),
      "Descriptives" = nrow(s3_MlCor_out) - ncol(s3_MlCor_out)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(s1_MlCor_out)) %>%
  pack_rows("Study 2", ncol(s1_MlCor_out) + 1,
            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out))) %>%
  pack_rows("Study 3", sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out)) + 1,  
            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out))) %>%
  pack_rows("Across Studies", sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out)) + 1,  
            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out), ncol(all_MlCor_out))) %>% # fix table position
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrOutWideAppB.tex")
